Additional Material

### 2016-01-13 paper/supplementary.Rnw
supplementary material

\title{Additional Material}

@@

\section{Subject Details}

@@

\begin{figure}[htbp]
\centering
<<choices, dependson='setup' =, echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
full.sub$choice_reason <-sapply(strsplit(as.character(unlist(full.sub$choice_reason)), "[^0-9]+"), "[[", 1)
ggplot(data=full.sub) + geom_bar(aes(x=choice_reason))
choice <- full.sub %>% transform(choice_reason= strsplit(as.character(choice_reason), "")) %>% unnest(choice_reason)
choice$rsgn <- factor(choice$rsgn, labels=c("r -","r +"))
choice$correct <- factor(choice$correct, labels=c("Did not detect", "Detected"))
ggplot(data=choice, aes(x=choice_reason, fill=correct)) + geom_bar() + facet_grid(design~rsgn) +
  theme(legend.position="bottom", axis.title=element_blank()) + scale_fill_discrete(name="True Plot")
@

\begin{figure}[htbp]
\centering 
<<avscore, dependson='setup' =, echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=LSE>>=  
subjplot <- summarise(group_by(full.sub, subj_id), eval=sum(weights), total = sum(score))
subjplot <- mutate(subjplot, avscore= total/eval)
ggplot(data=subjplot, aes(x=avscore)) + geom_histogram(binwidth=0.05)
@

\section{Multiple Selection}

\begin{figure}[htbp]
\centering
<<multiselect, dependson='setup' =, echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
m.select <- summarise(group_by(subset(full.sub, attempts>1), subj_id, pic_id), attempts=max(attempts))
m.freq <- data.frame(table(m.select$pic_id))
m.lineup <- merge(m.freq, Turk, by.x="Var1", by.y="pic_id")
ggplot(data=m.lineup) + geom_bar(aes(x=r, fill=plot), binwidth=0.2) + facet_grid(n~smoothed) + labs(y="Count", x="True plot correlation")
ggplot(data=subset(m.lineup, smoothed==1)) + geom_bar(aes(x=r, fill=plot), binwidth=0.2) + facet_wrap(~n)
@

\begin{table}
\caption{Number of selection per lineup evaluation. The subject with the most selections is also reported.}
\label{tabattempts}
<<tabattempts, dependson='setup' =, echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
attempts <- summarise(group_by(full.sub, subj_id, pic_id), attempts = max(attempts))
attempts.table <- data.frame(table(attempts$attempts))
attempts.table$most <- c(0,0,0,5,3,1,1)
colnames(attempts.table) <- c("Selections", "Whole Sample", "Subject 123")
kable(attempts.table, format="latex")
@
\end{table}

\begin{figure}[htbp]
\centering
<<multiattempts, dependson='setup' =, echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
ggplot(data=attempts) + geom_bar(aes(x=as.factor(attempts))) + labs(x="Number of selections", y=NULL)
@
\caption{Histogram of table~\ref{attempts}}
\label{attempts}
\end{figure}

>>>>

\if0\blind
{
\author{Nathaniel Tomasetti and Dianne Cook\\
Department of Econometrics and Business Statistics, Monash University\\
}
  \maketitle
} \fi
\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Supplementary Material: Comparing the Power of Plot Designs to Reveal Correlation}
\end{center}
  \medskip
} \fi

@@

\section{Subject Demographics}

@@

\section{Descriptive Statistics for Individuals}

\begin{figure}[htbp]
\centering
<<choices, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
full.sub$choice_reason <-sapply(strsplit(as.character(unlist(full.sub$choice_reason)), "[^0-9]+"), "[[", 1)
ggplot(data=full.sub) + geom_bar(aes(x=choice_reason))
choice <- full.sub %>% transform(choice_reason= strsplit(as.character(choice_reason), "")) %>% unnest(choice_reason)
choice$rsgn <- factor(choice$rsgn, labels=c("r -","r +"))
choice$correct <- factor(choice$correct, labels=c("Did not detect", "Detected"))
ggplot(data=choice, aes(x=choice_reason, fill=correct)) + geom_bar() + facet_grid(design~rsgn) +
  theme(legend.position="bottom", axis.title=element_blank()) + scale_fill_discrete(name="True Plot")
@

\begin{figure}[htbp]
\centering 
<<avscore, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>= 
subjplot <- summarise(group_by(full.sub, subj_id), eval=sum(weights), total = sum(score))
subjplot <- mutate(subjplot, avscore= total/eval)
ggplot(data=subjplot, aes(x=avscore)) + geom_histogram(binwidth=0.05)
@

\begin{figure}[htbp]
\centering
<<multiselect, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
m.select <- summarise(group_by(subset(full.sub, attempts>1), subj_id, pic_id), attempts=max(attempts))
m.freq <- data.frame(table(m.select$pic_id))
m.lineup <- merge(m.freq, bylineup, by.x="Var1", by.y="pic_id")
ggplot(data=m.lineup) + geom_bar(aes(x=r, fill=plot), binwidth=0.2) + facet_grid(n~smoothed) + labs(y="Count", x="True plot correlation")
ggplot(data=subset(m.lineup, smoothed==1)) + geom_bar(aes(x=r, fill=plot), binwidth=0.2) + facet_wrap(~n)
@

\begin{table}
\caption{Number of selections per lineup evaluation. The subject with the most selections is reported.}
\label{tabattempts}
<<tabattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
attempts <- summarise(group_by(full.sub, subj_id, pic_id), attempts = max(attempts))
attempts.table <- data.frame(table(attempts$attempts))
attempts.table$most <- c(0,0,0,5,3,1,1)
colnames(attempts.table) <- c("Selections", "Whole Sample", "Subject 123")
kable(attempts.table, format="latex")
@
\end{table}

\begin{figure}[htbp]
\centering
<<multiattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
ggplot(data=attempts) + geom_bar(aes(x=as.factor(attempts))) + labs(x="Number of selections", y=NULL)
@
\caption{Histogram of table~\ref{attempts}}
\label{attempts}
\end{figure}
